\section{ Pre-load actions  }
\subsection{ Operators }
Define an operator to handle numberic ranges
\call{Min to Max}.
\begin{Verbatim}
:- op(1,xfx, to).
\end{Verbatim}
and another one for DCGs.
\begin{Verbatim}
:- op(999,fx,><).
\end{Verbatim}
Here's one to handle failure-driven loops.
\begin{Verbatim}
:- op(1199,fx,all).
\end{Verbatim}
And here's one for defining tables.
\begin{Verbatim}
:- op(999,xfx,has).
\end{Verbatim}
\subsection{ Flags}
Index on the hash table access caches.
\begin{Verbatim}
:- discontiguous ht_cache/3.
:- index(ht_cache(1,1,0)).

:- discontiguous ht0/2.
\end{Verbatim}
Define an \call{inf}inity function. 
\begin{Verbatim}
:- arithmetic_function(inf/0).
\end{Verbatim}
Define a \call{rand}om function.
\begin{Verbatim}
:- arithmetic_function(rand/0).
\end{Verbatim}
Define a \call{rand(Min,Max)} function.
\begin{Verbatim}
:- arithmetic_function(rand/2).
\end{Verbatim}
Define a \call{rand(Min,Max,Mean)} function.
\begin{Verbatim}
:- arithmetic_function(rand/3).
\end{Verbatim}
Define a \call{normal} function.
\begin{Verbatim}
:- arithmetic_function(normal/2).
\end{Verbatim}
Define a \call{beta} function.
\begin{Verbatim}
:- arithmetic_function(beta/1).
\end{Verbatim}
Define a \call{gamma} function.
\begin{Verbatim}
:- arithmetic_function(gamma/2).
\end{Verbatim}
Add a ``left-justify'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('>',padChars(_,_)).
\end{Verbatim}
Add a ``right-justify'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('<',charsPad(_,_)).
\end{Verbatim}
Add a ``print squiggles'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('S',squiggle(_,_)).
\end{Verbatim}
Define a predicate for the lookup tables.
\begin{Verbatim}
:- discontiguous lookUp1/4.
:- multifile lookUp1/4.
:- index(lookUp1(1,1,1,0)).
\end{Verbatim}
\subsection{ Hooks}
A hook for lookup tables.
\begin{Verbatim}
term_expansion(Table has ColsRows , Out) :- 
    nonvar(ColsRows),
    ColsRows = (Cols+Rows),
    lookUpTable(Table=Cols+Rows,Out). 
\end{Verbatim}
Generate hook for all manner of expansions.
\begin{Verbatim}
term_expansion((:- make=Out,X),Out) :- X.
\end{Verbatim}
\subsection{ Hacks}
Some repairs to over-enthusiastic
DCG expansions to Prolog built-ins.
\begin{Verbatim}
goal_expansion(>=(A,B,C,C),        >=(A,B)).
goal_expansion(>(A,B,C,C),         >(A,B)).
goal_expansion(=(A,B,C,C),         =(A,B)).
goal_expansion(\=(A,B,C,C),        \=(A,B)).
goal_expansion(<(A,B,C,C),         <(A,B)).
goal_expansion(<=(A,B,C,C),        <=(A,B)).
goal_expansion(is(A,B,C,C),        is(A,B)).
goal_expansion(print(A,B,B),       print(A)).
goal_expansion(print(A,B,C,C),     print(A,B)).
goal_expansion(format(A,B,C,C),    format(A,B)).
goal_expansion(length(A,B,C,C),    length(A,B)).
goal_expansion(maplist(A,B,C,D,D), maplist(A,B,C)).
goal_expansion(><(A,B,B),          A).
\end{Verbatim}
