\section{ Pre-load actions  }
\subsection{ Operators }
Define an operator to handle numberic ranges
\call{Min to Max}.
\begin{Verbatim}
:- op(1,xfx, to).
\end{Verbatim}
\subsection{ Flags }
Define an \call{inf}inity function. 
\begin{Verbatim}
:- arithmetic_function(inf/0).
\end{Verbatim}
Define a \call{rand}om function.
\begin{Verbatim}
:- arithmetic_function(rand/0).
\end{Verbatim}
Define a \call{rand(Min,Max)} function.
\begin{Verbatim}
:- arithmetic_function(rand/2).
\end{Verbatim}
Define a \call{rand(Min,Max,Mean)} function.
\begin{Verbatim}
:- arithmetic_function(rand/3).
\end{Verbatim}
Define a \call{normal} function.
\begin{Verbatim}
:- arithmetic_function(normal/2).
\end{Verbatim}
Define a \call{beta} function.
\begin{Verbatim}
:- arithmetic_function(beta/1).
\end{Verbatim}
Define a \call{gamma} function.
\begin{Verbatim}
:- arithmetic_function(gamma/2).
\end{Verbatim}
Add a ``left-justify'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('>',padChars(_,_)).
\end{Verbatim}
Add a ``right-justify'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('<',charsPad(_,_)).
\end{Verbatim}
Add a ``print squiggles'' command to \call{format}.
\begin{Verbatim}
:- format_predicate('S',squiggle(_,_)).
\end{Verbatim}
Define a predicate for the lookup tables.
\begin{Verbatim}
:- discontiguous lookUp1/4.
:- multifile lookUp1/4.
:- index(lookUp1(1,1,1,0)).
\end{Verbatim}
\subsection{ Hooks }
A hook for lookup tables.
\begin{Verbatim}
term_expansion(Table = ColsRows , Out) :- 
    nonvar(ColsRows),
    ColsRows = (Cols+Rows),
    lookUpTable(Table=Cols+Rows,Out). 
\end{Verbatim}
