\documentclass[twocolumn,global]{svjour}
\usepackage{prod}\begin{document}

\theprogram{OMO} 
\thetocdepth{2} % e.g. 2
\thewp{~menzies/src/pl/prod/omo.pl}
\thepapers{refs}
\thetitle{Software cost estimation}
\theauthor{Tim Menzies}
\thereference{memo9@.ai.wvu.2003. 
            Available from 
            \url{http://tim.menzies.com/pdf/03omo.pdf}}
\theinstitute{Lane Department of Computer Science,
             West Virginia University,
             PO Box 6109, Morgantown,
             WV, 26506-6109, USA;\\
             \url{http://tim.menzies.us};
             \url{tim@menzies.us} 
             }
\theacknowledgement{his research was conducted at West Virginia
  University under NASA contract
  NCC2-0979 and NCC5-685.
  The work was sponsored by
  the NASA Office of Safety and Mission Assurance under the Software
  Assurance Research Program led by the NASA IV\&V Facility.  Reference
  herein to any specific commercial product, process, or service by
  trade name, trademark, manufacturer, or otherwise, does not constitute
  or imply its endorsement by the
United States Government.}
\theabstract{
COCOMO is a software effort estimation tool.
{\ME} is COCOMO written in SWI-Prolog~\cite{swiprolog}}

\section{ Warning!!!}

Contains deliberate error. Output should be:

\begin{LISTING}
COCOMO.ga says 1223.53 months (total);
28 staff over 45 months
\end{LISTING}

But show how that is all broken.

\begin{LISTING}
COCOMO.ga says 134588.0 months (total);
547 staff over 247 months
\end{LISTING}

What is wrong?

\section{ What is COCOMO?}
\input{cocomo}
\section{ Installation }\begin{Verbatim}
:- load_files([lib % grab standard stuff
              ,cfg % options controller
              ,gpl0, gpl1 % GPL-2 license stuff
              ,omo0 % pre-load actions
	      ,omolib % local libraries
              ,omo1 % predicates
              ,omo2 % start-up commands
	      ,omokb1 % example project file
	      ,ufp2sloc % function points per LOC database
              ],[silent(yes),if(changed)]).
\end{Verbatim}
\input{omo0}
\input{omo1}
\input{omo2}
\input{omolib}
\input{omokb1}

\section{ Bugs }
None known but many suspected.



\theend
\end{document}

